Results

### 2017-12-05 tmp-results.Rmd
save

```{r}
myggplot <- function(..., coeff = 1) {
  bigstatsr:::MY_THEME(ggplot(...), coeff = coeff)
} 
```

@@

```{r}
boot <- function(x, n = 1e5, f = mean) {
  sd(replicate(n, f(sample(x, replace = TRUE))))
}
```

>>>>

```{r}
myggplot <- function(..., coeff = 1) {
  bigstatsr:::MY_THEME(ggplot(...), coeff = coeff) +
  theme(strip.text.x = element_text(size = rel(2)),
        strip.text.y = element_text(size = rel(2)))
} 
```

@@

```{r}
boot <- function(x, n = 1e4, f = mean) {
  sd(replicate(n, f(sample(x, replace = TRUE))))
}
```
